---
title: "ggplotIntro"
subtitle: "Group: eta"  
author: 
  - "Yuheng Cui"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    self_contained: false 
    seal: false 
    lib_dir: libs
    css: ["xaringan-themer.css"]
    nature:
      highlightStyle: github
      highlightLanguage: r 
      highlightLines: true
      highlightSpans: false 
      countIncrementalSlides: false
      slideNumberFormat: '%current%/%total%'
      navigation:
        scroll: false 
        touch: true
        click: false
---

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#9E3E42",
  secondary_color = "#FF961C",
  inverse_header_color = "#fffff"
)
```

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(xaringanthemer)
library(xaringanExtra)
library(tidyverse)
```


background-image: url(https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcTZSHVUsnIGDV3Plqb_8Wrrn9aKJ_fphFe_-gMZ1ST0fiChySiS)
background-size: 350px
background-position: 88% 60%

# ggplotIntro Package

.pull-left[
<center>
<font size="5", style="font-family:cursive"> `r Sys.Date()` </font>
<br>
<br>
<font size="5", style="font-family:monaco"> Yuheng Cui (ycui0008) </font>
<center>
]


---
# Outline

#### What is the aim of `ggplotIntro` package?
#### What are the conponents of the package?
#### What does the shiny app look like and how to use it?
#### What are the possible improvements that could be done?

---

### Background

* Big data and data-driven decision-making are two important concepts also of growing importance (Provost & Fawcett, 2013).
* Data-driven decision-making is wildly used for prediction (e.g. energy companies).
* Data visualisation is fundamental within the field of statistics and data science.
* `ggplot2` package is basic package used for data visualisation

--
### Aim
* Motivate new `ggplot2` package learner
* Decrease the anxiety of learning `ggplot2`

---


# Gamification and Shiny app

.panelset[
.panel[.panel-name[Gamification]
* Interest was recognised as an independent factor and the desired outcome in the process of learning (Schiefele, 1991).
* Four general ways to increase intrinsic motivation (Lepper, 1988)
  + behavior undertaken for its own sake,
  + <font color = 'red'> for the enjoyment it provides </font>, 
  + the learning it permits, or 
  + <font color = 'red'> the feelings of accomplishment it evokes </font>.
* Educational games have been successfully used to teach many school subjects (Corbett et al., 2001).
* Students might be expected to have considerably better tolerance of discomfort but greater fears of failure; fear of failure may lead to <font color = 'red'> increased anxiety </font> and then to problems with tolerating these emotions (Harrington, 2005).
* In conclusion, the gamification can motivate new learners, increase the feelings of ownership and interactivity, and decrease the anxiety of learning.
]

.panel[.panel-name[Shiny app]

* It makes the gamification more manageable.
* Differentiate the project from other online tutorials
* In conclusion, the shiny app is more interactive and more like games.
]
]

---

# What are the components of the `ggplotIntro` package

* Two data sets: 

  + `who_covid`: WHO, covid-19 cases data till now
  + `GDP`: World Bank, GDP from 1966

* **Main body**: A shiny app
  + load the package, then use `launch_app()`

---
class: middle

<center>

# Introduction of the shiny app

---

# Possible improvements

.panelset[
.panel[.panel-name[Question bank]
**Random questions**
* Students benefit a little from rereading and restudying coherent and complex learning material (Callender & McDaniel, 2009). If the shiny app gives the same question to all learners every time, it is not beneficial for learners to restudying and reusing the exercises within the shiny app.
* Promotion of long-term retention is substantial, and the learning material should allow students to apply their knowledge in a variety of contexts (Ebersbach et al., 2020).


**Different difficulty levels**
* When playing games players enjoyed more, if the difficulty satisfied their gaming experience (Alexander et al., 2013).
* Offer questions of proper difficulty levels to learners.

]

.panel[.panel-name[Functions]

* Tidy the shiny app script.
* More convenient for question creation in the future.
* Less likely to make mistakes.
]
]


---
class: middle
<center>

# Thanks!



---
# Acknowledgement

This project would not have been possible without *Emi Tanaka*, the project supervisor, and *Mitchell O’Hara-Wild*. They helped a lot when developing the shiny app. The developer would also like to thank *Jessica Leung*.

Slides constructed with [`xaringan`](https://github.com/yihui/xaringan), [`knitr`](http://yihui.name/knitr) and [R Markdown](https://rmarkdown.rstudio.com),  [`xaringanExtra`](https://github.com/gadenbuie/xaringanExtra).

---
# Reference
<font size="2", style="font-family:cursive"> Alexander, J. T., Sear, J. & Oikonomou, A. (2013). An investigation of the effects of game difficulty on player enjoyment. Entertainment Computing, 4 (1), 53–62. </font>
<br>
<font size="2", style="font-family:cursive"> Callender, A. A. & McDaniel, M. A. (2009). The limited benefits of rereading educational texts. Contemporary Educational Psychology, 34 (1), 30–41. </font>
<br>

<font size="2", style="font-family:cursive"> Corbett, A. T., Koedinger, K. & Hadley, W. S. (2001). Cognitive tutors: From the research classroom to all classrooms. In Technology enhanced learning (pp. 215–240). Routledge. </font>
<br>

<font size="2", style="font-family:cursive"> Ebersbach, M., Feierabend, M. & Nazari, K. B. B. (2020). Comparing the effects of generating questions, testing, and restudying on students’ long-term recall in university learning. Applied Cognitive Psychology, 34 (3), 724–736. </font>
<br>

<font size="2", style="font-family:cursive"> Harrington, N. (2005). It’s too difficult! Frustration intolerance beliefs and procrastination. Personality and Individual Differences, 39 (5), 873–883. </font>
<br>

<font size="2", style="font-family:cursive"> Lepper, M. R. (1988). Motivational considerations in the study of instruction. Cognition and Instruction, 5 (4), 289–309. </font>
<br>

<font size="2", style="font-family:cursive"> Provost, F. & Fawcett, T. (2013). Data science and its relationship to big data and data-driven decision making. Big Data, 1 (1), 51–59. </font>
<br>

<font size="2", style="font-family:cursive"> Schiefele, U. (1991). Interest, learning, and motivation. Educational Psychologist, 26 (3-4), 299–323. </font>


---
class: center, middle

# Any questions?

```{r countdown, echo = FALSE}
countdown::countdown(minutes = 5, seconds = 0)
```
